%-------------------------
% Author : Arunav Dey
% Based off of: https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
% Resume
\begin{document}

\begin{center}
    \textbf{\Huge \scshape Arunav Dey} \\ \vspace{1pt}
    \small +91 897 162 2911 $|$ \href{mailto:arunav-dey@outlook.com}{\underline{arunav-dey@outlook.com}} $|$ 
    \href{https://github.com/ArunavDey}{\underline{github.com/ArunavDey}} $|$ \href{https://linkedin.com/in/arunav-dey}{\underline{linkedin.com/in/arunav-dey}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PES University}{Bengaluru, KA, India}
      {Bachelor of Technology; CGPA: \@8.7/10.0}{Jun. 2023, expected}
    \resumeSubheading
      {Christ Junior College}{Bengaluru, KA, India}
      {Pre-University in Science; Percentage: \@88.7\%}{May 2019}
    \resumeSubheading
      {Baldwin Boys' High School}{Bengaluru, KA, India}
      {ICSE in Science; Percentage: \@92.3\%}{May 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Web Development Intern}{Jan. 2023 -- Present}
      {Hiver}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Handled upgradation of a package from Node 16 to Node 18}
        \resumeItem{Developed the frontend for multiple features using React and Redux}
        \resumeItem{Worked on migrating BackboneJS code to ReactJS}
    \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Teaching Assistant}{Jan. 2023 -- Jun. 2023}
      {PES University}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Created coding problems related to Design and Analysis of Algorithms}
        \resumeItem{Created solutions for all such questions and included test cases}
      \resumeItemListEnd

    \resumeSubheading
      {Artificial Intelligence and Machine Learning Intern}{Jun. 2022 -- Aug. 2022}
      {Pronisi Inc.}{Bengaluru, KA, India}
      \resumeItemListStart
        \resumeItem{Explored human-pose models such as BlazePose}
        \resumeItem{Worked using Python libraries like OpenCV, MediaPipe and Torch}
        \resumeItem{Performed data collection and preparation using Python and FFmpeg}
        \resumeItem{Tested code using Pytest}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Discrimination of ADHD using LSTMCaps} $|$ \emph{Python, TensorFlow, Keras, MATLAB}}{Jan 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Created a Capsule-LSTM network for the deep learning model using TensorFlow and Keras}
            \resumeItem{Performed data cleaning and data preprocessing on the ADHD-200 dataset using MATLAB}
            \resumeItem{Used feature extraction techniques such as ReHo and fALFF using Python}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Photo to Painting using CycleGAN} $|$ \emph{Python, TensorFlow, Keras}}{Jan. 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{Implemented a CycleGAN model}
            \resumeItem{Trained the CycleGAN model to convert a photo to a painting using style transfer}
            \resumeItem{Collected and prepared data as paintings from multiple artists}
            \resumeItem{Explored Google Colab while training and using the model}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Railway Reservation System} $|$ \emph{Java, Spring, ReactJS}}{Jan. 2022 -- May 2022}
          \resumeItemListStart
            \resumeItem{Developed the backend using Spring and the frontend using ReactJS}
            \resumeItem{Used and explored SQLite for the database}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Food Delivery Web Application} $|$ \emph{NodeJS, ReactJS, ExpressJS, Firebase}}{Oct. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Developed the backend and middleware using NodeJS and ExpressJS}
            \resumeItem{Develoepd the frontend using React}
            \resumeItem{Used and explored Firebase for the database}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, HTML/CSS, C/C++, Java, PostgresQL} \\
     \textbf{Frameworks}{: MERN, NodeJS, FastAPI } \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, Google Cloud Platform, VS Code, Linux, Vim} \\
     \textbf{Libraries}{: ReactJS, Redux, pandas, NumPy, Matplotlib, TensorFlow, Keras}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
